Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-17 papers/clusters.tex
figure improvements
thanks

% figure shit
\newcommand{\insanefigure}[1]{%
\includegraphics[width=0.33\textwidth]{./figs/#1_MgFe.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_MgK.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_AlMg.png}\\
\includegraphics[width=0.33\textwidth]{./figs/#1_NaO.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_CN.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_SAl.png}\\
\includegraphics[width=0.33\textwidth]{./figs/#1_sky.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_decv.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_HR.png}}

@@

\acknowledgements
DWH was partially supported by
  the NSF (grants IIS-1124794, AST-1517237),
  NASA (grant NNX12AI50G), and
  the Moore-Sloan Data Science Environment at NYU.
This research made use of the NASA \project{Astrophysics Data System}.

>>>>

% figure shit
\newlength{\figwidth}\setlength{\figwidth}{0.3\textwidth}
\newcommand{\insanefigure}[1]{%
\includegraphics[width=\figwidth]{./figs/#1_MgFe.png}%
\includegraphics[width=\figwidth]{./figs/#1_MgK.png}%
\includegraphics[width=\figwidth]{./figs/#1_AlMg.png}\\
\includegraphics[width=\figwidth]{./figs/#1_NaO.png}%
\includegraphics[width=\figwidth]{./figs/#1_CN.png}%
\includegraphics[width=\figwidth]{./figs/#1_SAl.png}\\
\includegraphics[width=2\figwidth]{./figs/#1_gal.png}%
\includegraphics[width=\figwidth]{./figs/#1_HR.png}\\
\includegraphics[width=2\figwidth]{./figs/#1_vlon.png}}

@@

\acknowledgements
It is a pleasure to thank
  Jeremy Magland (SCDA), and
  Eddie Schlafly (LBNL)
for valuable discussions.
DWH was partially supported by
  the NSF (grants IIS-1124794, AST-1517237),
  NASA (grant NNX12AI50G), and
  the Moore-Sloan Data Science Environment at NYU.
This research made use of the NASA \project{Astrophysics Data System}.
